Differences from our PPoPP Conference Paper \cite{KBP16}

### 2019-01-14 latex/toms/algorithm.tex
Dim tree algorithm rough draft.
Initial BPP description commit

@@

In the case of updating the local factor matrix $\Mn{H}{n}_{\V{p}}$ we need to solve~\ref{eqn:nls} with $\M{X} = \Mn{H}{n}_{\V{p}}$, $\M{A} = \Mn{S}{n}$ and $\M{B} = \Mn{M}{n}_{\V{p}}$. Our framework is capable of supporting any alternating-updating NLS solver~\cite{KBP16}. The NLS solvers which fit this framework and are implemented in our software package are Multiplicative Update~\cite{LS99}, Hierarchical Alternating Least Squares~\cite{CP2009}, Block Principal Pivoting~\cite{KP2011}, Alternating Direction Method of Multipliers~\cite{HSL2016} and Nesterov-type algorithm~\cite{LKLHS2017}. We briefly describe the different solvers below. Note that the descriptions are for the general form of the NLS solver as shown in~\ref{eqn:nls}.

\subsubsection{Multiplicative Update (MU)}
The MU solve is an elementwise operation. The update rule for each element of $\M{X}$ is as follows,
\begin{align}
\M{X}(i,j) \leftarrow \M{X}(i,j)\frac{\M{B}(i,j)}{\left(\M{A}\M{X}\right)(i,j)}
\end{align}
While this rule does not solve~\ref{eqn:nls} to optimality it ensures a reduction in the objective value from the initial value of $\M{X}$.

@@

\subsubsection{Block Principal Pivoting (BPP)}
\subsubsection{Alternating Direction Method of Multipliers (ADMM)}
\subsubsection{Nesterov-type algorithm}

>>>>

\begin{algorithm}
\caption{Simple Dim Tree}
\label{alg:simpleDT}
\begin{algorithmic}
\Require $\T{X}$ is an $N$-way tensor, $n \in [N]$, $s$ split dimension, $n$ mode to compute MTTKRP for, projection tensor $\hat{\T{X}}$, ktensor $\hat{\T{Y}}$ corresponding to $\hat{\T{X}}$.

\If{n == 0 or n == N-1}
	\If{n = 0}
		\State $\M{K} \leftarrow KRP(s+1:N)$
		\State $\hat{\T{X}} \leftarrow \T{X}(0:s,s+1:N) \cdot \M{K}$
		\For{i=1:R}
			\State $\M{M}(:,i) \leftarrow \hat{\T{X}}_i(0,1:s) \cdot KRP(1:s)$
		\EndFor
	\Else % N-1 = n
		\State $\M{K} \leftarrow KRP(0:s)$
		\State $\hat{\T{X}} \leftarrow \Tr{X}(0:s,s+1:N)^\Tra \cdot \M{K}$
		\For{i=1:R}
			\State $\M{M}(:,i) \leftarrow \hat{\T{X}}_i(s+1,s+2:N) \cdot KRP(s+2:N)$
		\EndFor
	\EndIf
\
\Else
	\If{n $\leq$ s}
		\State Y = s
	\Else
		\State Y = N
	\EndIf
	\For{i=1:R}
		\State  $\M{K} \leftarrow KRP(n-1)$
		\State $\hat{\T{X}}_i \leftarrow \M{K}_i \cdot \hat{\T{X}}_i(n-1,n:Y)$ % Update to X
	\EndFor
	\For{i=1:R}
		\State  $\M{K} \leftarrow KRP(n+1:Y)$
		\State $\M{M}(:,i) \leftarrow \hat{\T{X}}_i(n,n+1:Y) \cdot \M{K}_i$
	\EndFor
\EndIf

\end{algorithmic}
\end{algorithm}

@@

In the case of updating the local factor matrix $\Mn{H}{n}_{\V{p}}$ we need to solve~\Cref{eqn:nls} with $\M{X} = \Mn{H}{n}_{\V{p}}$, $\M{A} = \Mn{S}{n}$ and $\M{B} = \Mn{M}{n}_{\V{p}}$. Our framework is capable of supporting any alternating-updating NLS solver~\cite{KBP16}. The NLS solvers which fit this framework and are implemented in our software package are Multiplicative Update~\cite{LS99}, Hierarchical Alternating Least Squares~\cite{CP2009}, Block Principal Pivoting~\cite{KP2011}, Alternating Direction Method of Multipliers~\cite{HSL2016} and Nesterov-type algorithm~\cite{LKLHS2017}. We briefly describe the different solvers below. Note that the descriptions are for the general form of the NLS solver as shown in~\Cref{eqn:nls}.

\subsubsection{Multiplicative Update (MU)}
The MU solve is an elementwise operation. The update rule for each element of $\M{X}$ is as follows,
\begin{align}
\M{X}(i,j) \leftarrow \M{X}(i,j)\frac{\M{B}(i,j)}{\left(\M{A}\M{X}\right)(i,j)}
\end{align}
While this rule does not solve~\Cref{eqn:nls} to optimality it ensures a reduction in the objective value from the initial value of $\M{X}$.

@@

\subsubsection{Block Principal Pivoting (BPP)}
BPP is an active-set like method for solving NLS problems. The main subroutine of BPP is the single right hand side version of~\Cref{eqn:nls},
\begin{align}
\V{x} \leftarrow \underset{\V{x} \ge 0}{\argmin} \left\lVert \M{A}\V{x} -\V{b}\right\rVert^2_F
\label{eqn:snls}
\end{align}
The Karash-Kuhn-Tucker (KKT) optimality conditions for~\Cref{eqn:snls} are shown below,
\begin{subequations}
\begin{align}
\V{y} &= \M{A}^\Tra\M{A}\V{x} - \M{A}^\Tra\V{b} \\
\V{y} &\geq \V{0} \\
\V{x} &\geq \V{0} \\
x_i y_i &= 0 \quad \forall i
\end{align}
\label{eqn:bppkkt}
\end{subequations}
The complementary slackness criteria from the KKT conditions forces the support sets, i.e. the non-zero elements, of $\V{x}$ and $\V{y}$ to be disjoint. This makes~\Cref{eqn:bppkkt} an instance of the \emph{Linear Complementarity Problem} which arises frequently in quadratic programming. When $k \ll \min(m.n)$, active-set methods are preferred since they deal with small matrices of size $m \times k$, $n \times k$ and $k \times k$. In the optimal solution, the active-set is the set of indices where $x_i = 0$ and the remaining indices are referred to as the passive set. Once the active-set is found, we can find the optimal solution to~\Cref{eqn:snls} by using solving an unconstrained least squares problem on the passive set of indices. The BPP algorithm attempts to find the active-set by greedily swapping indices between the intermediate active and passive sets until it finds a solution that satisfies the KKT conditions. Kim and Park discuss the method in greater detail in~\cite{KP2011}. The unconstrained least squares is solved using the Normal Equations method in the software though other methods can also be used.

\subsubsection{Alternating Direction Method of Multipliers (ADMM)}

\subsubsection{Nesterov-type algorithm}
